Hypertension and microbiome

### 2019-06-14 articletwo.Rmd
Missing kable

```{r lactobacillus prevalence}
pseq.genus %>%
    microbiome::transform(transform = "compositional") %>%
    prune_taxa(c("g_Lactobacillus"), .) %>%
    psmelt %>%
    spread(OTU, Abundance) %>%
    dplyr::mutate(lacto.prevalent = ifelse(g_Lactobacillus > 0.001, TRUE, FALSE),
                  duna.present = ifelse(is.na(NA.), 0, 1)) %>%
    group_by(duna.present) %>%
    summarize(lacto_detected = sum(lacto.prevalent), n = n(), ratio = lacto_detected/n)
```

>>>>

```{r lactobacillus prevalence}
pseq.genus %>%
    microbiome::transform(transform = "compositional") %>%
    prune_taxa(c("g_Lactobacillus"), .) %>%
    psmelt %>%
    spread(OTU, Abundance) %>%
    dplyr::mutate(lacto.prevalent = ifelse(g_Lactobacillus > 0.001, TRUE, FALSE),
                  duna.present = ifelse(is.na(NA.), 0, 1)) %>%
    group_by(duna.present) %>%
    summarize(lacto_detected = sum(lacto.prevalent), n = n(), ratio = lacto_detected/n) %>%
    kable
```
